---
title: "Diamond prices"
author: "Hector Mario Romer"
date: '2022-02-26'
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

Diamonds prices depend on their weight, measured in carats. But carats are not the only factor in pricing. Prices also depend on:

- Cut: quality of the diamond from best to worst (Ideal, Premium, Very Good, Good, Fair)
- Color: best(D) to worst(J)
- Clarity: measures how clear the diamond is from best to worst (IF, VVS2, VVS1, VS2, VS1, SI2, SI1, I1)

This application predicts diamond prices based on input values.

## Summary

The "diamonds" dataset is found in the ggplot2 R package. It contains almost 54,000 observations (diamonds). 
```{r include=FALSE}
library(ggplot2)
library(dplyr)
data(diamonds)
dim(diamonds)
```

Let's take a look at following table. It shows the amounts of diamonds per cut and color

```{r}
table(diamonds$cut, diamonds$color)
```


## Plot

The application will allow you to tweak the following plot:

```{r plot, echo = FALSE}
info <- diamonds %>% filter(cut == "Ideal", color == "D", clarity == "IF")
p <- ggplot(data = info, aes(x = carat, y = price)) +
        theme_bw() +
        geom_point() +
        geom_smooth(formula = y ~ x, method = "lm") +
        labs(title = "Diamond Prices (in US dollars)",
             xlab = "Carat", ylab = "Price")
        
p
```

## Final words

Use the controls on the left to tweak the plot. Move the carat slider to get a prediction for the diamond price. The app will automatically react to your inputs.


Enjoy!!!
